Performance of two different ontological and data access methods

### 2014-07-02 cold2014/magnus.tex
minor clean
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@713 43ef1190-90fd-4dd7-a769-d0121f02b80e

If we take another look at Table \ref{10factorEffect} we see that
there are only three single factors except O that are in the top 15
significant factors.  After the 15 significant factor the absolute
effect drops significantly. The three factors are E, FC and T. E and T
are present because of the same reasons as in the six factor
experiment. We also see in the top 15 that there are only these three
factors present in all the factor interactions as well, which
indicates that T, FC and E affects each other. This is logical because
if a car has a high fuel consumption it also has a high emission
rate. There are some possible explanations for why there are so many
significant factor interactions in some of the experiments. The order
will affect this as mention above. Another explanation is that we
chose an average value to be an upper and lower limit of a factor. We
used these as factor levels to avoid an unrealistic high number of
levels. This could have opened for more new specifications to check on
one level of the factor.  As we see in the Table
\vref{10factorEffect}, \textit{E:WT} is higher than \textit{WT}
itself. This might indicate that one of the levels of E will open up
for more values to traverse in one of the levels of WT. This is a
complex matter which will depend on each product model as well as the
interaction between the specifications.

@@

% TODO: In conclusion, discuss external validity.

>>>>

If we take another look at Table \ref{10factorEffect} we see that
there are only three single factors except O that are in the top 15
significant factors.  After the 15 significant factor the absolute
effect drops significantly. The three factors are E, FC and T. E and T
are present because of the same reasons as in the six factor
experiment. We also see in the top 15 that there are only these three
factors present in all the factor interactions as well, which
indicates that T, FC and E affects each other. This is to be expected
because if a car has a high fuel consumption it also has a high
emission rate. There are some possible explanations for why there are
so many significant factor interactions in some of the
experiments. The order will affect this as mention above. Another
explanation is that we chose an average value to be an upper and lower
limit of a factor. We used these as factor levels to avoid an
unrealistic high number of levels. This could have opened for more new
specifications to check on one level of the factor.  As we see in the
Table \vref{10factorEffect}, \textit{E:WT} is higher than \textit{WT}
itself. This might indicate that one of the levels of E will open up
for more values to traverse in one of the levels of WT. This is a
complex matter which will depend on each product model as well as the
interaction between the specifications.

@@
